Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-22 prob.tex
From: Tai, Yu-Tsung Sent: Monday, August 22, 2016 3:58 To: Ortiz, Gerardo <ortizg@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Liu, Weihua <liuweih@indiana.edu> Subject: RE: can't come Mon am
Dear all, 

Fix almost everything pointed out last time, and scratch two possible
approaches to complete the story at the very end… Don’t know which one
is better or neither? 

Besides, Weihua Liu is interested in our research… so I invited him to
join our meeting next time…
He is a new post-doctor in Math, and has some backgrounds in quantum
probability, qu

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
meaning of convex interval-valued probability measures...? If there
is a good explanation, we may only consider convex interval-valued
probability measures, and replace the definition in the beginning...?}}
\end{itemize}
\qed\end{definition}

@@

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393},
or an elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$
onto a linear subspace~$S$ of $\Hilb$. The set of all events~$\events$
can be defined recursively as follow: \footnote{``Projection'' is sometimes called ``orthogonal projection\textquotedbl{}
or ``self-adjoint projection\textquotedbl{} to emphasize $P^{\dagger}=P$~\cite{Griffiths2003,Maassen2010}.} 
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_{1}$ and $P_{2}$ are \emph{orthogonal} if
$P_{1}P_{2}=P_{2}P_{1}=\mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal,
where the preposing subscript $\mathscr{O}$ means $\tensor*[_{\mathscr{O}}]{+}{}$
is an operation between operators. 
\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
\end{itemize}
\qed\end{definition}

@@

\begin{example}[One-qubit quantum probability space] Consider
a one-qubit Hilbert space with states $\ket{\phi}$, which can be
expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
$\alpha,\beta\in\C$. The set of events associated with this Hilbert
space consists of all projection operators. Each event is interpreted
as a possible post-measurement state of a quantum system in current
state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
indicates that the post-measurement state will be $\ket{1}$; the
event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
indicates that the post-measurement state will be a linear combination
of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
that the post-measurement state will be the empty state. As in the
classical case, a probability measure is a function that maps events
to $[0,1]$: here is a partial specification of a possible probability
measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}

@@

\subsection{Measuring Quantum Probabilities Ideally: Radon-Nikodym and Gleason's
Theorem}

@@

Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
we can pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
and fix a density matrix~$\rho$ representing in the same basis,
i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
Applying the canonical inner product, we can define a Radon-Nikodym
derivative~$f_{\rho}:\Omega\rightarrow[0,1]$ by
\begin{equation}
f_{\rho}\left(\ket{\psi_{j}}\right)=\ip{\psi_{j}}{\rho\psi_{j}}=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
\end{equation}
Furthermore, we only consider the quantum events~$\events'$ with
the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$,
where $E\in2^{\Omega}$. The classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
induced by the Radon-Nikodym derivative~$f_{\rho}$ is exactly the
Born rule of the mixed state~$\rho$~\cite{Maassen2010}, 
\begin{equation}
\pmeas'\left(E\right)\overset{\left(\ref{eq:Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum f_{\rho}\left(\ket{\psi_{j}}\right)\overset{\left(\ref{eq:quantum-Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}=\Tr\left(\rho P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\mu_{\rho}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed-1}
\end{equation}

In this sense, the Radon-Nikodym derivative~$f_{\rho}$ is a special
case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
in Hilbert spaces of dimension $d\geq3$, given a quantum probability
measure $\mu$, there exist a mixed state~$\rho$ that induces such
a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend definition~\ref{def:QuantumProbabilitySpace}
to the following corollary.

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of
dimension $d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$
satisfying the conditions listed in definition~\ref{def:QuantumProbabilitySpace},
there exists an unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{cor}

@@

Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. Therefore, we should plug in the
definition of interval-valued probability measure into the definition
of quantum probability space for each ideal measurement. More specifically,
for classical probability measures, definition~\ref{def:ClassicalProbabilitySpace}
and lemma~\ref{lem:classicalProbabilityMeasure} are almost the same
except the last condition using the equal sign~$=$ in real-valued
definition~\ref{def:QuantumProbabilitySpace} and the subset equal
sign~$\subseteq$ in interval-valued lemma~\ref{lem:classicalProbabilityMeasure}.
Therefore, for quantum probability measures, replacing the the equal
sign~$=$ in real-valued definition~\ref{def:QuantumProbabilitySpace}
by the subset equal sign~$\subseteq$ gives the only reasonable definition
for quantum interval-valued probability measures as follow.

@@

\begin{definition}~Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \mu:\events\rightarrow[0,1]\textrm{ quantum probability measure}\middle|\mu\left(P\right)\in\bar{\mu}\left(P\right)\forall P\in\events\right\} $.
\item $\bar{\mu}$ is called convex if 
\begin{equation}
\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
 for all commuting $P_{1},P_{2}\in\events$. 
\end{itemize}
\qed\end{definition}

@@

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story might go to section~\ref{sec:DQT}.
The problem of this approach is that Because we don't really use $\mathbb{C}$
in example~\ref{ex:three-dimensional-three-value}, I could expect
example~\ref{ex:three-dimensional-three-value} is likely to serve
as an counterexample for discrete interval-valued Gleason's theorem...

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach might go to section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. More precisely, we might need to verify tensor product
and quantum teleportation works in this model...}

@@

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some extra-conditions
to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.

Following are possible extra-conditions:
\begin{enumerate}
\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
too small...
\item $\mu\otimes\mu$ is not a quantum real-valued probability measure,
where $\mu$ is a non-Born real-valued probability measure for dimension
2. Maybe embedding the small space into the bigger one could add extra-conditions
to kill strange interval-valued probability measures?
\end{enumerate}

@@

In CQT, an time evolution operator~$U$ will map a state~$\ket{\phi}$
to $U\ket{\phi}$. In this case, its quantum real-valued probability
measure after evolution is
\[
\mu_{U\ket{\phi}}^{B}\left(P\right)=\ip{\phi}{U^{\dagger}PU\phi}=\mu_{\ket{\phi}}^{B}\left(U^{\dagger}PU\right)\textrm{ .}
\]
Hence, given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
the quantum interval-valued probability measure after time evolution
operator~$U$ is defined as 
\[
\bar{\mu}_{U}\left(P\right)=\bar{\mu}\left(U^{\dagger}PU\right)\textrm{ .}
\]

@@

Might be hard, because $\mu\otimes\mu$ is not a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.

\yutsung{Quantum Fubini Theorem?}

@@

$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
that a quantum real-valued probability measure can be considered as
an special case of quantum interval-valued probability measure.

>>>>

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
meaning of convex interval-valued probability measures...? If there
is a good explanation, we may only consider convex interval-valued
probability measures, and replace the definition in the beginning...?}}
\end{itemize}
\qed\end{definition}

@@

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393},
or an elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$
onto a linear subspace~$S$ of $\Hilb$. The set of all events~$\events$
can be defined recursively as follow: \footnote{``Projection'' is sometimes called ``orthogonal projection\textquotedbl{}
or ``self-adjoint projection\textquotedbl{} to emphasize $P^{\dagger}=P$~\cite{Griffiths2003,Maassen2010}.} 
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_{1}$ and $P_{2}$ are \emph{orthogonal} if
$P_{1}P_{2}=P_{2}P_{1}=\mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal,
where the preposing subscript $\mathscr{O}$ means $\tensor*[_{\mathscr{O}}]{+}{}$
is an operation between operators. 
\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ with an
orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
\end{itemize}
\qed\end{definition}

@@

\begin{example}{[}One-qubit quantum probability space{]} Consider
a one-qubit Hilbert space with states $\ket{\phi}$, which can be
expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
$\alpha,\beta\in\C$. The set of events associated with this Hilbert
space consists of all projection operators. Each event is interpreted
as a possible post-measurement state of a quantum system in current
state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
indicates that the post-measurement state will be $\ket{1}$; the
event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
indicates that the post-measurement state will be a linear combination
of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
that the post-measurement state will be the empty state. As in the
classical case, a probability measure is a function that maps events
to $[0,1]$. Here is a partial specification of a possible probability
measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}

@@

\subsection{Measuring Quantum Probabilities Ideally: From Radon-Nikodym to Gleason's
Theorem}

@@

Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
we can pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
and fix a density matrix~$\rho$ representing in the same basis,
i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
Applying the canonical inner product, we can define a Radon-Nikodym
derivative~$f_{\rho}:\Omega\rightarrow[0,1]$ by
\begin{equation}
f_{\rho}\left(\ket{\psi_{j}}\right)=\ip{\psi_{j}}{\rho\psi_{j}}=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
\end{equation}
Furthermore, we only consider the quantum events~$\events'$ with
the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$,
where $E\in2^{\Omega}$. The classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
induced by the Radon-Nikodym derivative~$f_{\rho}$ is exactly the
Born rule of the mixed state~$\rho$~\cite{Maassen2010}, 
\begin{equation}
\pmeas'\left(E\right)\overset{\left(\ref{eq:Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum f_{\rho}\left(\ket{\psi_{j}}\right)\overset{\left(\ref{eq:quantum-Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}=\Tr\left(\rho P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\mu_{\rho}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed-1}
\end{equation}

In this sense, the Radon-Nikodym derivative~$f_{\rho}$ is a special
case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

\begin{thm}{[}Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}{]}\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, there exists an unique mixed
state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{thm}

@@

Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. Therefore, we should plug in the
definition of interval-valued probability measure into the definition
of quantum probability space for each ideal measurement. More specifically,
for classical probability measures, definition~\ref{def:ClassicalProbabilitySpace}
and lemma~\ref{lem:classicalProbabilityMeasure} are almost the same
except the last condition using the equal sign~$=$ in real-valued
definition~\ref{def:ClassicalProbabilitySpace} and the subset equal
sign~$\subseteq$ in interval-valued lemma~\ref{lem:classicalProbabilityMeasure}.
Therefore, for quantum probability measures, replacing the the equal
sign~$=$ in real-valued definition~\ref{def:QuantumProbabilitySpace}
by the subset equal sign~$\subseteq$ gives the only reasonable definition
for quantum interval-valued probability measures.

@@

\begin{definition}~Given a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{quantum probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $.
\item $\bar{\mu}$ is called convex if 
\begin{equation}
\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{1}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
 for all commuting $P_{1},P_{2}\in\events$. 
\end{itemize}
\qed\end{definition}

@@

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story is scratched in section~\ref{sec:DQT}.
The problem is the discrete version of example~\ref{ex:three-dimensional-three-value}.
Because we don't really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
the discrete version of example~\ref{ex:three-dimensional-three-value}
is likely to serve as an counterexample for discrete interval-valued
Gleason's theorem... Hence, we may need to put some extra-conditions
to by-pass the discrete version of example~\ref{ex:three-dimensional-three-value}.

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach is scratched in section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. For example, we might need to verify tensor product
and quantum teleportation works in this model...}

@@

Discrete interval-valued Gleason's theorem should be here, but it
is unlikely to work if the discrete version of example~\ref{ex:three-dimensional-three-value}
works... Might need to put some extra-conditions to by-pass it...

Following are possible extra-conditions:
\begin{enumerate}
\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
too small...
\item $\mu\otimes\mu$ might not be a quantum real-valued probability measure,
where $\mu$ is a non-Born real-valued probability measure for dimension
2. Maybe embedding the small space into the bigger one could add extra-conditions
to kill strange interval-valued probability measures?
\end{enumerate}

@@

In CQT, an time evolution operator~$U$ will map a state~$\ket{\phi}$
to $U\ket{\phi}$. In this case, its quantum real-valued probability
measure after evolution is
\[
\mu_{U\ket{\phi}}^{B}\left(P\right)=\ip{\phi}{U^{\dagger}PU\phi}=\mu_{\ket{\phi}}^{B}\left(U^{\dagger}PU\right)\textrm{ .}
\]
Hence, given any quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
the quantum interval-valued probability measure after time evolution
operator~$U$ should be defined as 
\[
\bar{\mu}_{U}\left(P\right)=\bar{\mu}\left(U^{\dagger}PU\right)\textrm{ .}
\]

@@

Might be hard, because $\mu\otimes\mu$ might not be a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.

Quantum Fubini Theorem?

@@

$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
that a quantum real-valued probability measure can be considered as
an special case of quantum interval-valued probability measure...
